Warming Degrees and Flowering Trees

### 2025-04-03 paper/paper.qmd
fixed minor citation misspelling

The earlier flowering of sakura represents a classic example of phenological mismatch—where interacting species respond differently to climate cues, potentially disrupting ecological relationships. @Gérard2020 highlight that "many phenological shifts have already been reported at the species level for the insect emergence or blooming time of flowering plants", with temperature being the predominant driver. However, these shifts are rarely uniform across different ecological levels, creating potential desynchronization between plants and their pollinators or other dependent species.

>>>>

The earlier flowering of sakura represents a classic example of phenological mismatch—where interacting species respond differently to climate cues, potentially disrupting ecological relationships. @Gerard2020 highlight that "many phenological shifts have already been reported at the species level for the insect emergence or blooming time of flowering plants", with temperature being the predominant driver. However, these shifts are rarely uniform across different ecological levels, creating potential desynchronization between plants and their pollinators or other dependent species.
